---
title: "Rare Species Selection"
author: "Josie Lesage"
date: "3/12/2020"
output: html_document
---

```{r setup, include=FALSE}
library("tidyverse")
```

# Background and goals
This document aims to help us select which species to include in our rare species search as we map trails in the Thomas Fire scar.  

We will draw on data from the CCH-1 and CCH-2 databases, CNDDB, Cal-IPC, etc. 

For CCH-1 records, use the "lat and long" style search, then follow along and download as a tab-delimited file. 

# Data Import
```{r data import}
cnps_list <- read.csv("CNPS_Rares_SB_Ventura.csv")
cnddb <- read.csv("CNDDB_Thomas_Fire.csv")
cch1 <- read.csv("CCH1.csv") %>%
  rename(Scientific.Name = Scientific_Name)
```

```{r merge tables and export}
cch1_rares <- left_join(cch1, cnps_list, by="Scientific.Name") %>%
  filter(!is.na(CRPR))

write.csv(cch1_rares, "CCH1_Rares_TF.csv")
```





# ArcGIS

## Importing a CSV
Import by going to file -> add data -> add XY data -> browse to CSV's house
The standard online download format is World - WGS 1984

Take the temporary events file - and export the data from whatever format it was brought in as and turn it into a shapefile. Name as desired and put into a geodatabase. YOU MUST DO THIS BEFORE YOU CLIP. You can't clip from the raw data - you must convert it to a shapefile and add to GBD first.

## To clip
You have to go to "select by layer" and answer the questions for select by location or feature.

## Merging data
Load data into the GBD shapefile if you need to merge two things (like SB and Ventura counties).


# To Do 
CCH2 - download all species records, clip to fire, and limit to rares/weeds
CCH1 - filter to just weeds

Create overall species list - consider filtering by habitat type
